On classification of integral point sets and particular upper bounds for their minimal diameter in higher dimensions \footnote{ This work was carried out at Voronezh State University and supported by Russian Science Foundation grant 19-11-00197. }

### 2021-11-09 AvdMomZvol_rails/Article.tex
[AMZr] Rename the paper
[AMZr] Hopefully the last fix

\title{
	On particular diameter bounds for integral point sets in higher dimensions
	\footnote{
		This work was carried out at Voronezh State University and supported by Russian Science
		Foundation grant 19-11-00197.
	}
}

@@

@@

\begin{remark}
	Every centered-circular point set has characteristic 1.
	Indeed, let $\mathcal{P} = \{M_0, M_1,$ $ M_2, M_3, ..., M_k\}$ be a centered-circular point set
	with $M_0$ being the center.
	According to the sine formula, in the triangle $M_1 M_2 M_3$
	\begin{equation}
		\sin \angle M_1 M_2 M_3 = \frac{|M_1M_3|}{2R}
		,
	\end{equation}
	where $R = |M_0 M_1| $ is the radius of the triangle's circumcircle.
	Then the area of the triangle $M_1 M_2 M_3$ is
	\begin{equation}
		S = \frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \sin \angle M_1 M_2 M_3 =
		\frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \frac{|M_1M_3|}{2|M_0 M_1|} \in\mathbb Q
		.
	\end{equation}
\end{remark}

>>>>

\title{
	On classification of integral point sets and particular upper bounds for their minimal diameter in higher dimensions
	\footnote{
		This work was carried out at Voronezh State University and supported by Russian Science
		Foundation grant 19-11-00197.
	}
}

@@

This paper is an extended version of preprint~\cite{avdeev2019particular}.

@@

\begin{remark}
	Every centered-circular point set has characteristic 1.
	Indeed, let $\mathcal{P} = \{M_0, M_1,$ $ M_2, M_3, ..., M_k\}$ be a centered-circular point set
	with $M_0$ being the center.
	by the Law of sines, in the triangle $M_1 M_2 M_3$
	\begin{equation}
		\sin \angle M_1 M_2 M_3 = \frac{|M_1M_3|}{2R}
		,
	\end{equation}
	where $R = |M_0 M_1| $ is the radius of the triangle's circumcircle.
	Then the area of the triangle $M_1 M_2 M_3$ is
	\begin{equation}
		S = \frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \sin \angle M_1 M_2 M_3 =
		\frac12 |M_2 M_1| \cdot |M_2 M_3| \cdot \frac{|M_1M_3|}{2|M_0 M_1|} \in\mathbb Q
		.
	\end{equation}
\end{remark}
